Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/pilot.tex
added pilot selection order

>>>>

For the sake of analysis, the selection order of the ballots sampled during the pilot was also recorded. Figure~\ref{fig:pilot_sequence} shows the cumulative tally of winner ballots after each new ballot in the selection order is added to the sample. We observe two interesting phenomena in this particular sample's selection order. First, an SO \BRAVO audit of this sample stops because the \BRAVO condition is met when the sample (orange line) surpasses the minimum number of winner ballots (blue line) earlier in the sample.\footnote{Such cases also provide insight into how \Providence is a tighter test in expectation because SO \BRAVO ignores information from the rest of the sample after the \BRAVO condition is met at some point earlier in the selection order.} EoR \BRAVO, however, does not stop. It might be difficult to explain to the public why SO \BRAVO stops in more extreme cases like this where the condition is met early in the sample but poor evidence for the alternative hypothesis in the rest of the sample is ignored. Secondly, after the first $11$ ballots were drawn, only $5$ of them were for the announced winner, giving misleading evidence due to a too-small sample size. Both these ideas are addressed more thoroughly in Section~\ref{sec:workload}.
%first draft, needed to be shorter: ...stopping condition for the cumulative tally at the end of the round would see that the \BRAVO condition is not met (and would be correct that an EoR \BRAVO audit would require a second round for this sample). On the other hand, an SO \BRAVO audit does stop already in the first round because the cumulative sample met the \BRAVO stopping condition at some point before all the ballots had been added to the sample. In Figure~\ref{fig:pilot_sequence}, this is seen when the observed sample (orange) line touches (or goes above) the minimum winner ballots (blue) line which gives the \BRAVO stopping condition (i.e. a \BRAVO condition is met whenever the number of winner ballots in the sample is at least the number indicated by that blue line). While relatively rare, there also possible cases of selection order where the SO \BRAVO condition is met very early but then bad luck is had thereafter and the ultimate cumulative sample at the end of the round gives very poor evidence that the announced tally is correct. There could even be fewer ballots for the winner than the loser. Such cases might be difficult for an election official to explain to the public, especially when the evidence at the end of the round provides poor support for the alternative hypothesis.\footnote{Such cases also provide insight into how \Providence is a tighter test in expectation because SO \BRAVO ignores information from the rest of the sample after the \BRAVO condition is met at some point earlier in the selection order.} In Section~\ref{sec:workload} we address such cases more thoroughly.

\begin{figure}
\includegraphics[width=.5\textwidth]{pilot_sequence.png}
\caption{For each sample size from $1$ to $140$, the intermediate cumulative sum of ballots for the announced winner found in the sample is shown.}
\label{fig:pilot_sequence}
\end{figure}

### 2022-10-11 providence/sections/workload.tex
added pilot selection order

\begin{figure}
\includegraphics[width=.5\textwidth]{misleading_limits.png}
\caption{The proportion of simulated \Providence audits that had a \emph{misleading sample} in any round.}
\label{fig:misleading}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=.5\textwidth]{misleading_limits.png}
\caption{The proportion of simulated \Providence audits for the Virginia contest parameters that had a \emph{misleading sample} in any round.}
\label{fig:misleading}
\end{figure}

We observe a similar behavior in our simulations of audits on the contest from the pilot audit. Figure~\ref{fig:pilot_misleading} shows the proportion of the pilot simulations which contained a \emph{misleading sample} in any round. Despite the large difference in margin ($\sim 5\%$ in Virginia and $\sim 25\%$ in the pilot) we still observe that a \emph{misleading limit} of $0.01$ is first achieved at roughly $p=0.8$ and $0.001$ at $p=0.95$.

\begin{figure}
\includegraphics[width=.5\textwidth]{pilot_misleading_prop.png}
\caption{The proportion of simulated \Providence audits for the pilot audit parameters that had a \emph{misleading sample} in any round.}
\label{fig:pilot_misleading}
\end{figure}
